Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-27 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
small change

For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs
of slowly-rotating BHs, and found that for the axial gravitational-led modes the damping time increases, as we
increase $\ell_{\rm dCS}$, at constant BH spin.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
this is the branch of QNMs we choose to work with.

>>>>

For dCS gravity, we follow Ref.~\cite{Wagle:2021tam}, which numerically calculated the QNMs
of slowly-rotating BHs, and found that for the axial gravitational-led modes the damping time increases, as we
increase $\ell_{\rm dCS}$, at constant, small BH spin.
%
Hence, according to the prescription of Sec.~\ref{sec:theory_specific_qnm},
this is the branch of QNMs we choose to work with.
